Mining Historical Advertisements in Digitized Newspapers

### 2020-04-13 ms/article.tex
added link to codebase

The analysis in this section is based on the metadata of the national newspaper \textit{Trouw} (1946-1995).\footnote{For most of the examples in this chapter, direct access to the metadata and newspaper data is required. Researchers can contact KB for API access to the newspapers.} An initial exploratory data analysis shows that the dataset contains instances of bad segmentation, in which small parts of advertisements appeared as separate advertisements. To exclude these segmentation errors from the dataset, we filtered out ads with a width or height smaller than 100 pixels. After removing these advertisements, \textit{Trouw} contains about 1.31 million advertisements for the period 1945-1995. From Figure~\ref{fig:ad_curve}, we can gauge that the total number of advertisements increased between 1946 and 1995, with a sudden increase in the early 1980s. Alongside this increase in the number of ads, we also see a sudden, albeit slight decrease in the size of the advertisements (Figure~\ref{fig:mean_size}). We plotted took the $log_{10}$ of the mean size to visualize the rate of change better.

@@

For this section, we charted six product nationalities associated with cigarettes: American, British, Egyptian, Russian, Turkish, and Virginia.\footnote{We approach Virginia as a nationality, since the term came to represent Britain} Using regular expressions, we queried the singular and plural variants of these references as well as common spelling variations.\footnote{Code is available on \textbf{XXX}} The occurrence of these words in advertisements serves as a proxy for the popularity of cigarettes with varying product nationalities. Figure~\ref{fig:cig_nationality} shows the relative frequency of references to nationalities per 1,000 cigarette advertisements.

>>>>

The analysis in this section is based on the metadata of the national newspaper \textit{Trouw} (1946-1995).\footnote{For most of the examples in this chapter, direct access to the metadata and newspaper data is required. Researchers can contact KB for API access to the newspapers. Code is available on: \url{https://github.com/melvinwevers/eldorado}} An initial exploratory data analysis shows that the dataset contains instances of bad segmentation, in which small parts of advertisements appeared as separate advertisements. To exclude these segmentation errors from the dataset, we filtered out ads with a width or height smaller than 100 pixels. After removing these advertisements, \textit{Trouw} contains about 1.31 million advertisements for the period 1945-1995. From Figure~\ref{fig:ad_curve}, we can gauge that the total number of advertisements increased between 1946 and 1995, with a sudden increase in the early 1980s. Alongside this increase in the number of ads, we also see a sudden, albeit slight decrease in the size of the advertisements (Figure~\ref{fig:mean_size}). We plotted took the $log_{10}$ of the mean size to visualize the rate of change better.

@@

For this section, we charted six product nationalities associated with cigarettes: American, British, Egyptian, Russian, Turkish, and Virginia.\footnote{We approach Virginia as a nationality, since the term came to represent Britain} Using regular expressions, we queried the singular and plural variants of these references as well as common spelling variations. The occurrence of these words in advertisements serves as a proxy for the popularity of cigarettes with varying product nationalities. Figure~\ref{fig:cig_nationality} shows the relative frequency of references to nationalities per 1,000 cigarette advertisements.
